Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-28 Ben_Manuscripts/Paper1/Outline.tex
updates to BCC topology and BCC initialization procedure

  We will now address the questions raised in the introduction in the order
  that they were asked.  %BJC: Not a fan of this

@@

  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
  %MRS: I think things have changed since then? 
  The disordered basin shares little in common with the ordered basin but 
  its long term stability suggests that it can exist under some conditions.  
  Basin B is the dominant configuration at higher temperatures.
  \begin{itemize}
        \item We linearly ramped the temperature of a system in Basin A
        from 280K to 340K over 100 ns.
        \item Visually, there is a distinct change in pore structure from one
        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
        Basin B (Figure~\ref{fig:340K_pore}).
        \item The slope of all order parameters changes between 315K and 325K
        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
        possibility of an abrupt change in system ordering.
        \item Our 100 ns temperature ramp was likely too fast and caused the system
        to suffer from hysteresis.
  \end{itemize}

@@

  In an attempt to mitigate hysteresis, we performed a slow, stepwise temperature ramp.
  \begin{itemize}
        \item Starting from a sandwiched structure equilibrated at 280K, the system
        temperature was raised to 300K and allowed to equilibrate for 200 ns.
        \item At the end of 200 ns, the temperature was raised 5K and equilibrated
        again for 200 ns.
        \item We continued raising the temperature by 5K and equilibrating for 200 ns
        until the system was equilibrated for 200 ns at 320K.
	\item The same process was repeated with a system equilibrated in Basin B and used
	as a benchmark for comparison. 
  \end{itemize}

@@

  Basin A and Basin B are two configurationally metastable basins.
  \begin{itemize}
        \item There is litle change in disordered phase properties during the 
        temperature ramp.
	\item We observed smooth changes in order parameters as temperature
        of the Basin A system was increased implying that we cannot claim the
	existence of two phases (Figure~\ref{fig:phase_transition}).
	\item Qualitatively, the pore structure of the Basin A system becomes
        comparable to one characteristic of Basin B as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
	\item The Basin A system does not converge to the same order parameter
	values as Basin B, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
	\item To resolve the quanitative discrepancy, we would need a slower 
	temperature ramp
	\item Since there are no abrupt changes in any order parameter along the 
	trajectory, we can conclude that the two basins are not separate phases
	\item Basin A is the closest match to what is seen experimentally
	\item Basin B is likely an intermediate between the Col\textsubscript{h} 
	phase and isotropic phase
	\item Basin B is present in our simulations at lower temperatures 
        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
	stabilize the system into Basin A. 
  \end{itemize}

@@

  %MRS: which model? Be specific as to which of the above structural ensembles was used.
  The model gives reasonable estimates of ionic conductivity when compared to 
  experiment.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Table~\ref{table:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
	\item Collective diffusion calculations were generated from 
	500 ns simulations.
	\item Our calculated values would benefit from longer simulations. 
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
	\item We hypothesize that conductivity is enhanced in Basin B due to a 
	higher sodium ion diffusivity.
	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
	Sodium ions have less nearby sites to move to in Basin A.
	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
	\item In both cases, our calculated values for Basin A are higher than the 
	experimental values, as expected. 
	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
	\item However, the real system, although mostly aligned and straight, has a 
	distribution of azimuthal angles, meaning that the pores have a degree of 
	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
	fold increase in ionic conductivity. We would expect additional gains in a 
	perfectly aligned system.
  \end{itemize}

@@

  %MRS: the next sections maybe should be supporting?
  %MRS: you say ``the distance decreases by 1 A'' but is that true
  %over all of the different structures? 
  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
  \subsection*{Implementation of the crosslinking algorithm}

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  Basin A.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.
	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
	crosslinked
	\item Major features are still present in the X-ray diffraction
	\item The ionic conductivity is higher/lower in the crosslinked system
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}

>>>>

  We will now address the questions raised in the introduction in the order
  that they were asked.  %BJC: Not a fan of this transition

@@

  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
  %MRS: I think things have changed since then? 
  The disordered basin shares little in common with the ordered basin but 
  its long term stability suggests that it can exist under some conditions.  
  We observed that Basin B is the dominant configuration at higher temperatures.
  \begin{itemize}
        \item We linearly ramped the temperature of a system in Basin A
        from 280K to 340K over 100 ns.
        \item Visually, there is a distinct change in pore structure from one
        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
        Basin B (Figure~\ref{fig:340K_pore}).
        \item The slope of all order parameters changes between 315K and 325K
        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
        possibility of an abrupt change in system ordering.
        \item Our 100 ns temperature ramp was likely too fast and caused the system
        to suffer from hysteresis.
  \end{itemize}

@@

  In an attempt to mitigate hysteresis, we performed slow, stepwise temperature ramps
  on a parallel displaced and a sandwiched configuration previously equilibrated at 300K.
  \begin{itemize}
        \item Every 200 ns, the temperature was raised 5K until we reached 345K
	\item We performed the same procedure with a system equilibrated in the CP Basin
	and used it as a benchmark for comparison. 
  \end{itemize}

@@

  The CP and OP basins are two configurationally metastable basins.
  \begin{itemize}
        \item There is litle change in disordered phase properties during the 
        temperature ramp.
	\item We observed smooth changes in order parameters as temperature
        of the Basin A system was increased implying that we cannot claim the
	existence of two phases (Figure~\ref{fig:phase_transition}).
	\item Qualitatively, the pore structure of the OP basin system becomes
        comparable to one characteristic of the CP basin as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
	\item The OP basin system does not converge to the same order parameter
	values as the CP basin, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
	\item To resolve the quanitative discrepancy, we would need a slower 
	temperature ramp
	\item Since there are no abrupt changes in any order parameter along the 
	trajectory, we can conclude that the two basins are not separate phases
	\item The OP basin is the closest match to what is seen experimentally
	\item The CP basin is likely an intermediate between the Col\textsubscript{h} 
	phase and isotropic phase
	\item The CP basin is present in our simulations at lower temperatures 
        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
	stabilize the system into the OP basin. 
  \end{itemize}

@@

  We use the equilibrated offset system in the OP basin to calculate ionic 
  conductivity since its structure is the closest match to experiment.
  The model gives reasonable estimates of ionic conductivity when compared to 
  experiment.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Table~\ref{table:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
	\item Collective diffusion calculations were generated from 
	500 ns simulations.
	\item Our calculated values would benefit from longer simulations. 
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
  \end{itemize}

  The CP basin has a higher ionic conductivity than the OP basin.
  \begin{itemize}
	\item We hypothesize that conductivity is enhanced in Basin B due to a 
	higher sodium ion diffusivity.
	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
	Sodium ions have less nearby sites to move to in Basin A.
	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
	\item In both cases, our calculated values for Basin A are higher than the 
	experimental values, as expected. 
	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
	\item However, the real system, although mostly aligned and straight, has a 
	distribution of azimuthal angles, meaning that the pores have a degree of 
	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
	fold increase in ionic conductivity. We would expect additional gains in a 
	perfectly aligned system.
  \end{itemize}

@@

  %MRS: the next sections maybe should be supporting?
  %MRS: you say ``the distance decreases by 1 A'' but is that true
  %over all of the different structures?
  %BJC: limiting the discussion to the OP basin in the offset configuration 
  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
  \subsection*{Implementation of the crosslinking algorithm}

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  the OP basin.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.
	\item We reach 95 \% conversion of terminal vinyl groups
	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
	crosslinked
	\item Major features are still present in the X-ray diffraction
	\item The ionic conductivity is higher/lower in the crosslinked system
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}
